Tropical Andes plant occurrence data GBIF

### 2023-10-18 code/L0/L0_TropicalAndes_frugivores_GBIF.Rmd
add code to extract lat and long from geometry and convert to dataframe

# Load required packages
```{r}
library(dplyr)
library(rgbif) 
```

@@

# Crop occurrence data to forest extent
```{r}
TropicalAndes_frugivore_occ_forest <- TropicalAndes_frugivore_occ[Forest_sf,]
```

>>>>

# Load required packages
```{r}
library(dplyr)
library(rgbif) 
library(sf)
```

@@

# Crop occurrence data to forest extent
```{r}
TropicalAndes_frugivore_occ_forest <- TropicalAndes_frugivore_occ[TropicalAndes_IUCNHabitat_Forest,]
```

## Extract lat and long to seperate columns
```{r}
TropicalAndes_frugivore_occ_forest <- TropicalAndes_frugivore_occ_forest %>%
    mutate(decimalLongitude = sf::st_coordinates(.)[,1],
           decimalLatitude = sf::st_coordinates(.)[,2])
```

```{r}
TropicalAndes_frugivore_occ_forest <- as.data.frame(TropicalAndes_frugivore_occ_forest)
```

### 2023-10-18 code/L0/L0_TropicalAndes_plants_GBIF.Rmd
add code to extract lat and long from geometry and convert to dataframe

# Crop occurrence data to forest extent
```{r}
TropicalAndes_plant_occ_forest <- TropicalAndes_plant_occ[Forest_sf,]
```

>>>>

# Crop occurrence data to forest extent
```{r}
TropicalAndes_plant_occ_forest <- TropicalAndes_plant_occ[TropicalAndes_IUCNHabitat_Forest,]
```

## Extract lat and long to seperate columns
```{r}
TropicalAndes_plant_occ_forest <- TropicalAndes_plant_occ_forest %>%
    mutate(decimalLongitude = sf::st_coordinates(.)[,1],
           decimalLatitude = sf::st_coordinates(.)[,2])
```

```{r}
TropicalAndes_plant_occ_forest <- as.data.frame(TropicalAndes_plant_occ_forest)
```
